|

### 2025-05-23 doc/paper.qmd
table caption added

# Function to prep LaTeX table
def prep_latex_table(df, caption=None, label=None):
    df = escape_special_characters(df.reset_index(drop=True))
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)
    latex_table = df.to_latex(
        column_format=column_format,
        index=False,
        float_format=custom_float_format,
    )
    latex_table_lines = [
        "\\begin{table}",
        "\\centering",
        "\\resizebox{\\textwidth}{!}{%",
        latex_table,
        "}",
        f"\\caption{{{caption}}}" if caption else "",
        f"\\label{{{label}}}" if label else "",
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

```{python}
#| label: tbl-gapminder2007_summary
#| tbl-cap: "Summary Statistics by Continent (Gapminder 2007)"
#| echo: false
#| output: asis

print(prep_latex_table(summary))
print("\n\\caption*{\\textnormal{This table reports the mean and median life expectancy and GDP per capita, along with the total population and number of countries per continent for the year 2007.}}")
```

>>>>

# Function to prep LaTeX table
# Function to prep LaTeX table with optional description
def prep_latex_table(df, caption=None, label=None, description=None):
    df = escape_special_characters(df.reset_index(drop=True))
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)

    latex_table = df.to_latex(
        column_format=column_format,
        index=False,
        float_format=custom_float_format,
        escape=False
    )

    latex_caption = f"\\caption{{{caption}}}" if caption else ""
    latex_description = f"\\caption*{{\\textnormal{{{description}}}}}" if description else ""
    latex_label = f"\\label{{{label}}}" if label else ""

    latex_table_lines = [
        "\\begin{table}",
        "\\centering",
        "\\resizebox{\\textwidth}{!}{%",
        latex_table,
        "}",  # End resizebox
        latex_caption,
        latex_description,
        latex_label,
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

```{python}
#| label: tbl-gapminder2007_summary
#| tbl-cap: "Summary Statistics by Continent (Gapminder 2007)"
#| echo: false
#| output: asis
#| 
print(prep_latex_table(
    summary,
    description="\\fontsize{10pt}{12pt}\\selectfont This table reports the mean and median life expectancy and GDP per capita, along with the total population and number of countries per continent for the year 2007."
))
```
